Investigation of the activities performed by experimental researchers in a software engineering lab using an ethnographic methodology

### 2024-06-25 tex/appendix.tex
Tercera revisision completada (v4)

\appendices
\section{Acronyms}

\begin{table}[h]
	\caption{Acronyms used in the manuscript}
	\label{table}
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{|p{25pt}|p{115pt}|p{25pt}|}
	\hline
	Item & Term & Acronym\\
	\hline
	1 & Empirical Software Engineering & ESE\\
	\hline
	2 & Research Group Under Study & RGUS\\
	\hline
	3 & Grupo de Investigación en Modelos de Producción de Software e Industria Inteligente & GrIMPSoftII\\
	\hline
	4 & Research Manager & RM\\
	\hline
	5 & Experiment Manager & EM\\
	\hline
	6 & Senior Experimenter & SrEx\\
	\hline
	7 & Experimental Process Model & EPM\\
	\hline
	8 & Experimental Process Workflow & EPW\\
	\hline
	\multicolumn{3}{p{251pt}}{These acronyms have been used throughout the manuscript.}\\
	\end{tabular}
	\label{tab1}
\end{table}

>>>>

\appendices

\section{Acronyms}

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[h]
\small
\center
\caption{Acronyms used throughout the manuscript}
\label{tab:acronyms}
\begin{tabular}{ll}
\hline
\multicolumn{1}{c}{Acronym} & \multicolumn{1}{c}{Term}       \\ \hline
\added[id=v4]{EM}                          & \added[id=v4]{Experiment Manager}             \\ 
\added[id=v4]{EPM}                         & \added[id=v4]{Experimental Process Model}     \\ 
\added[id=v4]{EPW}                         & \added[id=v4]{Experimental Process Workflow}  \\ 
\added[id=v4]{ESE}                         & \added[id=v4]{Empirical Software Engineering} \\ 
\added[id=v4]{RGUS}                        & \added[id=v4]{Research Group Under Study}     \\ 
\added[id=v4]{RM}                          & \added[id=v4]{Research Manager}               \\ 
\added[id=v4]{SE}                          & \added[id=v4]{Software Engineering}           \\ 
\added[id=v4]{SrEx}                        & \added[id=v4]{Senior Experimenter}            \\ \hline 
\end{tabular}
\end{table}

### 2024-06-25 tex/introduction.tex
Tercera revisision completada (v4)

\section{Introduction}\label{sec-introduction}
Replication is troublesome in general \cite{Klein-2018-many}, particularly in the social and life sciences \cite{Pashler-2012-perspectives,Baker-2016-lid-reproducibility}. In Empirical Software Engineering (ESE)\added[id=v3]{, there is a consensus that replications are important \cite{shepperd2018role}, but} the number of replications is small \cite{Bezerra-2015-Replication-SE-U-SMS} and the rate of confirmation of previous results is limited \cite{Jorgensen-2016-Incorrects-Results-SEE}.

>>>>

\section{Introduction}\label{sec-introduction}
Replication is troublesome in general \cite{Klein-2018-many}, particularly in the social and life sciences \cite{Pashler-2012-perspectives,Baker-2016-lid-reproducibility}. In Empirical Software Engineering (ESE%
\footnote{\added[id=v4]{The acronyms used throughout the paper are listed in Table~\ref{tab:acronyms} in the appendix.}}%
)\added[id=v3]{, there is a consensus that replications are important \cite{shepperd2018role}, but} the number of replications is small \cite{Bezerra-2015-Replication-SE-U-SMS} and the rate of confirmation of previous results is limited \cite{Jorgensen-2016-Incorrects-Results-SEE}.

### 2024-06-25 tex/research-method.tex
Tercera revisision completada (v4)

Ethnography identifies details that are ignored by \deleted[id=v2]{or in} other method\replaced[id=v2]{ologies, including Artificial Intelligence (AI) \cite{yadav2023development}}{s}. The disadvantage is the time required for learning \cite{Sharp-2016-Ethnographic-Studies-ESE}. Thus, we opted to study a single experimental research group over a long period instead of working halfway with several experimental research groups over shorter periods. This decision was also motivated by the challenge of finding several open-minded experimental research groups willing to participate in this research. We selected a representative, i.e., respected and well-known, research group to guarantee (to the extent possible) the reliability of the results, their validity, and the findings' scientific significance \cite{sjoberg-2007-future-empical-methods}.

@@

\subsection{Research documentation}\label{sub-sec-research-documentaition}
The raw data obtained in this study is organized as shown in Figure \ref{fig-info-study}. The tree represents a repository of around 20GB of information. The repository contains pictures, recordings, models, reports, and transcriptions, most in Spanish (the operational language used during the research). Spanish is widespread enough to utilize the repository with little effort. The final products, e.g., models, have been translated into English to improve the reader's understanding. The repository is not public because it contains personal data. However, upon request, the corresponding author will share the repository with interested researchers.

>>>>

Ethnography identifies details that are ignored by \deleted[id=v2]{or in} other method\replaced[id=v2]{ologies, including Artificial Intelligence \cite{yadav2023development}}{s}. The disadvantage is the time required for learning \cite{Sharp-2016-Ethnographic-Studies-ESE}. Thus, we opted to study a single experimental research group over a long period instead of working halfway with several experimental research groups over shorter periods. This decision was also motivated by the challenge of finding several open-minded experimental research groups willing to participate in this research. We selected a representative, i.e., respected and well-known, research group to guarantee (to the extent possible) the reliability of the results, their validity, and the findings' scientific significance \cite{sjoberg-2007-future-empical-methods}.

@@

\subsection{Research documentation}\label{sub-sec-research-documentaition}
The raw data obtained in this study is organized as shown in Figure \ref{fig-info-study}. The tree represents a repository of around 20 GB of information. The repository contains pictures, recordings, models, reports, and transcriptions, most in Spanish (the operational language used during the research). Spanish is widespread enough to utilize the repository with little effort. The final products, e.g., models, have been translated into English to improve the reader's understanding. The repository is not public because it contains personal data. However, upon request, the corresponding author will share the repository with interested researchers.
